### 2018-02-10 Writing/Thesis/content/chapter-conclusion.tex
more writing
More writing & some clean-up

% Move from specific to general
% Use existing literature for confirmation, contradiction, comparison
% "Speak to introduction"
\chapter{Conclusion}
\label{sec:conclusion}
% Introductory restatement of research problems, aims / reseach question -> remin of problem + purpose and how addressed
In this thesis, the problem of predicting a ranking of classification algorithms for a new data set on the basis of meta features of the data set and past performances of the algorithms has been considered. Being able to predict a ranking of such algorithms is desirable since this potentially speeds up and simplifies the process of algorithm selection, which is important due to a rapidly increasing amount of available data, and more importantly, data that is available but has not yet been analyzed. The problem has been addressed by implementing to different approaches, regression-based and preference-based ranking, and the evaluations of both against each other, a baseline and an oracle.

@@

% Practical applications / limitations: assess value / relevance / implications: What does it mean for theory, what for practice
On the basis of the results, it can be concluded that a causal connection exists between certain meta features of a data set and the predictive accuracy of classification algorithms for this data set, which can be exploited to a degree by regression models and label ranking models to predict a ranking of classification algorithms. A practical application of these findings may be to incorporate the implementation or parts of it in another Auto-ML tool as a search heuristic, similar to how some Auto-ML solutions like AUTO-SKLEARN already benefits from meta learning \cite{feurer2015efficient}. However, some additional work may have to be done in extension to this thesis in order for a sensible integration.

% Recommendations for future work
\section{Future Work}
\label{sec:conclusion:future}
%- more careful training by hand-selecting datasets for training (but then aains is this really the real world anymore? But then again duplicates may be contained)

>>>>

% Move from specific to general
% Use existing literature for confirmation, contradiction, comparison
% "Speak to introduction"
\chapter{Conclusion}
\label{sec:conclusion}
% Introductory restatement of research problems, aims / reseach question -> remin of problem + purpose and how addressed
In this thesis, the problem of predicting a ranking of classification algorithms for a new data set on the basis of meta features of the data set and past performances of the algorithms has been considered. Being able to predict a ranking of such algorithms is desirable since this potentially speeds up and simplifies the process of algorithm selection, which is important due to a rapidly increasing amount of available data, and more importantly, data that is available but has not yet been analyzed. The problem has been addressed by implementing to different approaches, regression-based and preference-based ranking. Both have been evaluated extensively against a baseline and an oracle.

@@

% Practical applications / limitations: assess value / relevance / implications: What does it mean for theory, what for practice
On the basis of these results, it can be concluded that a causal connection exists between certain meta features of a data set and the predictive accuracy of classification algorithms for this data set, which can be exploited to a degree by regression models and label ranking models to predict a ranking of classification algorithms. A practical application of these findings may be to incorporate the implementation or parts of it in another Auto-ML tool as a search heuristic, similar to how some Auto-ML solutions like AUTO-SKLEARN already benefits from meta learning \cite{feurer2015efficient}. However, some additional work may have to be done in extension to this thesis in order for a sensible integration.

% Recommendations for future work
\section{Future Work}
\label{sec:conclusion:future}
% Has worked reasonably well -> extend evaluation

%- more careful training by hand-selecting datasets for training (but then aains is this really the real world anymore? But then again duplicates may be contained)

### 2018-02-10 Writing/Thesis/content/chapter-evaluation.tex
More writing & some clean-up

@@

\subsection{Time}
\hspace{-1em}
\begin{table}[h]
	\begin{tabularx}{1.1\textwidth}{>{\hsize=2.6\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Build Time (ms)} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Prediction Time (ms)} \\ \cline{2-9}
										& Min		& Max		& Mean		& Stdv 	& Min	& Max		& Mean		& Stdv 	\\ \hline
		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	& 0 		& 86.667 	& 3.469	 	& 7.244 	\\
		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	& 0 		& 82.353 	& 3.78	 	& 6.535	\\	
		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	& 0		& 60 		& 3.097 		& 5.745	\\	
		REPTree			 				& 599 		& 1264 		& 629		& 38 	& 0 		& 82.353		& 4.829	 	& 7.948	\\	
		InstanceBased 					& 66 		& 550 		& 90	 		& 25 	& 0 		& 82.353		& 5.401 		& 9.44	\\	
		InstanceBased\footnotemark{}		& 66 		& 138 		& 88	 		& 12 	& 0 		& 98.367 	& 5.437 		& 10.323	\\	
		InstanceBased\footnotemark{}		& 66 		& 163		& 87	 		& 12 	& 0 		& 82.353 	& 5.382	 	& 9.402	\\	
		PairwiseComparison 				& 11784 		& 15096		& 12623	 	& 348 	& 0 		& 97.822 	& 9.762	 	& 13.135	\\	
		BestAlgorithm	 				& 193	 	& 321		& 221	 	& 23	 	& 0		& 82.353		& 6.480 		& 10.168	\\							
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Build and Prediction Times of the Rankers in ms}
\end{table}

@@

\begin{table}[h]
	\begin{tabularx}{1.1\textwidth}{>{\hsize=2.6\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Build Time (ms)} \\ \cline{2-5}
										& Min		& Max		& Mean		& Stdv 	\\ \hline
		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	\\
		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	\\	
		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	\\	
		REPTree			 				& 599 		& 1264 		& 629		& 38 	\\								
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Root Mean Square Error of Predicted Performance Values for the Regression-Based Rankers}
\end{table}

>>>>

\hspace{-1em}
\begin{table}[h]
	\begin{tabularx}{1.1\textwidth}{>{\hsize=1.6\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X}
		Ranker 					& \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{Kendall's Rank Correlation} & \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{Loss} & \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{BestThreeLoss}\\ \cline{2-7} 
										& Mann-Whitney U & P-Value & Mann-Whitney U	& P-Value & Mann-Whitney U & P-Value \\ \hline
		LinearRegression 				& 186381.5 & 2.702E-109 & 126861.5 & 7.694E-12 & 129028.0 & 1.327E-13 \\
		M5P				 				& 186236.0 & 6.230E-109 & 118828.5 & 1.840E-6 & 126379.5 & 1.821E-11 \\
		RandomForest		 			& 187750.5 & 9.737E-113 & 128853.5 & 1.861E-13 & 129037.0 & 1.304E-13 \\
		REPTree			 				& 181228.0 & 8.094E-97 & 111850.0 & 0.003 & 118793.0 & 1.926E-6 \\		
		InstanceBased					& 142665.5 & 8.818E-28 & 109372.0 & 0.020 & 104279.0 & 0.311 \\
		InstanceBased\footnotemark{}	& 166460.5 & 2.583E-65 & 111940.5 & 0.003 & 109211.0 & 0.022 \\
		InstanceBased\footnotemark{} 	& 166031.0 & 1.715E-64 & 110675.5 & 0.008 & 106223.0 & 0.130 \\
		PairwiseComparison				& 110610.0 & 0.008 & 120547.5 & 1.848E-7 & 107728.0 & 0.057
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Significance of Results Regarding Kendall Rank Correlation Coefficient}
\end{table}

@@

\subsection{Time}
\hspace{-1em}
\begin{table}[h]
	\begin{tabularx}{1.1\textwidth}{>{\hsize=2.6\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Build Time (ms)} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Prediction Time (ms)} \\ \cline{2-9}
										& Min		& Max		& Mean		& Stdv 	& Min	& Max		& Mean		& Stdv 	\\ \hline
		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	& 0 		& 86.667 	& 3.469	 	& 7.244 	\\
		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	& 0 		& 82.353 	& 3.78	 	& 6.535	\\	
		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	& 0		& 60 		& 3.097 		& 5.745	\\	
		REPTree			 				& 599 		& 1264 		& 629		& 38 	& 0 		& 82.353		& 4.829	 	& 7.948	\\	
		InstanceBased 					& 66 		& 550 		& 90	 		& 25 	& 0 		& 82.353		& 5.401 		& 9.44	\\	
		InstanceBased\footnotemark{}		& 66 		& 138 		& 88	 		& 12 	& 0 		& 98.367 	& 5.437 		& 10.323	\\	
		InstanceBased\footnotemark{}		& 66 		& 163		& 87	 		& 12 	& 0 		& 82.353 	& 5.382	 	& 9.402	\\	
		PairwiseComparison 				& 11784 		& 15096		& 12623	 	& 348 	& 0 		& 97.822 	& 9.762	 	& 13.135	\\	
		BestAlgorithm	 				& 193	 	& 321		& 221	 	& 23	 	& 0		& 82.353		& 6.480 		& 10.168	\\							
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Build and Prediction Times of the Rankers in ms (full meta data)}
\end{table}

@@

\begin{table}[h]
	\begin{tabularx}{\textwidth}{>{\hsize=1.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Root Mean Square Error} \\ \cline{2-5}
										& Min		& Max		& Mean		& Stdv 	\\ \hline
		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	\\
		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	\\	
		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	\\	
		REPTree			 				& 599 		& 1264 		& 629		& 38 	\\								
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Root Mean Square Error of Predicted Performance Values for the Regression-Based Rankers (full meta data)}
\end{table}
